---
title: 'Untitled'
author: 'Bruno Caneco'
date: '23/02/2022'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Modules

```{r cars}
library(shiny)
library(sCRM)

tbp_wf_App <- function(){

  ui <- shinydashboardPlus::dashboardPage(
    
    shinydashboardPlus::dashboardHeader(),
    shinydashboardPlus::dashboardSidebar(),
    dashboardBody(
      golem_add_external_resources(),
      mod_pnl_wf_ui('wf-1', is_demo = TRUE, band_mode = FALSE, wf_label = "wf 1")
    )
  )

  server <- function(input, output, session) {
    mod_pnl_wf_server(id = 'wf-1', band_mode = reactive(FALSE), is_demo = TRUE, wf_id = "wf_1", wf_tp_id = "tp-wf-1")
  }
  
  shinyApp(ui, server)
}

tbp_wf_App()
```



```{r}
library(shiny)

turb_oper_app <- function(){
  
  ui <- fluidPage(
    golem_add_external_resources(),
    
    mod_trbn_oper_ui(id = "toper_test"),
  )
  
  server <- function(input, output, session) {
    
    mod_trbn_oper_server(
      id = "toper_test",
      band_mode = reactive(FALSE),
      is_demo = TRUE
      )
  }
  
  shinyApp(ui, server)
  
}

turb_oper_app()
```




```{r}
library(shiny)

prob_input_app <- function(){
  ui <- fluidPage(
    
    golem_add_external_resources(),
    
    fluidRow(
      col_6(
        mod_prob_inputs_ui(
          id = "input_1", 
          #pars_lkp = spp_biopars_lookup
          pars_lkp = wf_pars_lookup %>%
            filter(par_name %in% c("bld_pitch", "rtn_speed")), 
          band_mode = TRUE
        )
      )
    )
  )
  
  server <- function(input, output, session) {
    
    mod_prob_inputs_server(
      id = "input_1", 
      pars_lkp = wf_pars_lookup %>%
                    filter(par_name %in% c("bld_pitch", "rtn_speed")),
      #pars_lkp = spp_biopars_lookup,
      band_mode = reactive(TRUE)
    )
  }
  
  shinyApp(ui, server)
  
}

prob_input_app()
```





```{r}

library(shiny)

test_app <- function(determ){
  ui <- fluidPage(
    golem_add_external_resources(),
    mod_test_ui(id = "test_1")
  )
  
  server <- function(input, output, session) {
    mod_test_server("test_1", determ = determ)
  }
  
  shinyApp(ui, server)
  
}

test_app(determ = reactive(TRUE))

```





```{r}
library(shiny)

spp_pnl_app <- function(){
  
   ui <- shinydashboardPlus::dashboardPage(

    shinydashboardPlus::dashboardHeader(),
    shinydashboardPlus::dashboardSidebar(),
    dashboardBody(
      golem_add_external_resources(),
      fluidRow(
        column(
          12,
          mod_pnl_spp_ui(
            id = "Common_Guillemot", 
            spp_label = "Common Guillemot",
            band_mode = FALSE, wf_label = "Demo")
        )
      )
    )
   )

  
  server <- function(input, output, session) {
    
     rv_inputs <- reactiveValues()
    
    mod_pnl_spp_server(
      id = "Common_Guillemot", 
      spp_label = "Common Guillemot", 
      band_mode = reactive(FALSE), 
      wf_id = "demo", 
      spp_id = "guill", 
      scrm_inputs = rv_inputs)
  }
  
  shinyApp(ui, server)
  
}

spp_pnl_app()

```





```{r}
library(shiny)

spp_in_wf_app <- function(){
  
  ui <- fluidPage(
    golem_add_external_resources(),
    
    mod_spp_in_wf_ui(id = "pnl-sppinwf-tavira"),
  )
  
  server <- function(input, output, session) {
    
    mod_spp_in_wf_server(
      id = "pnl-sppinwf-tavira",
      band_mode = reactive(TRUE), 
      wf_label = "Tavira"
      )
  }
  
  shinyApp(ui, server)
  
}

spp_in_wf_app()
```



```{r}
library(shiny)
library(shinydashboard)

completeness_app <- function(){
  
   ui <- shinydashboardPlus::dashboardPage(
    
    shinydashboardPlus::dashboardHeader(),
    shinydashboardPlus::dashboardSidebar(),
    dashboardBody(
      golem_add_external_resources(),
      fluidRow(
        col_3(
          shinyWidgets::progressBar(
            id = "pb42",
            value = 20,
            #display_pct = TRUE,
            size = "sm",
            status = "danger",
            striped = FALSE,
            title = "Completeness",
            commas = TRUE
          ),
          p("y missing x errors(s)")
        )
      ),
      fluidRow(
        col_3(
          p(strong("Completeness")),
          flexdashboard::gaugeOutput("gauge", width = "50%")
        )
      )
    )
  )

  server <- function(input, output, session) {
    
    output$gauge <- flexdashboard::renderGauge({
      
      flexdashboard::gauge(
        value = 42, 
        min = 0, 
        max = 100, 
        symbol = '%', 
        label = "y missing\nx error(s)",
        flexdashboard::gaugeSectors(
          success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
        ))
      
    })
  
  }
  
  
  shinyApp(ui, server)
  
}

completeness_app()
```




```{r}
library(shiny)
library(zeallot)

fhd_inputs_app <- function(){
  
  ui <- fluidPage(
    golem_add_external_resources(),
    mod_fhd_inputs_ui(id = "fhd_1")
  )
  
  server <- function(input, output, session) {
    
    #c(fhd_iv, gen_fhd, surv_fhd) %<-% mod_fhd_inputs_server(
    c(fhd_iv, fhd) %<-% mod_fhd_inputs_server(
      id = "fhd_1",
      spp_label = "gcaixota", #"Common Guillemot",
      band_mode = reactive(FALSE)
    )
    
    observe({
      #browser()
      fhd
      fhd_iv$validate()
    })
    
  }
  
  shinyApp(ui, server)
}

fhd_inputs_app()

```




```{r cars}
library(shiny)

output_panel_App <- function(){

  ui <- shinydashboardPlus::dashboardPage(
    
    shinydashboardPlus::dashboardHeader(),
    shinydashboardPlus::dashboardSidebar(),
    dashboardBody(
      golem_add_external_resources(),
     
       mod_sim_outputs_ui(
        id = "outputs",
        scrm_outputs = reactive(iris)
      )
      
      # shinyWidgets::verticalTabsetPanel(
      #   id = "vtabwf_2",
      #   contentWidth = 11,
      #   color = "#434C5E",
      #   shinyWidgets::verticalTabPanel(
      #     title = ""
      #   )
      # )
      
    )
  )

  server <- function(input, output, session) {

    mod_sim_outputs_server(
      id = "outputs",
      scrm_inputs = reactiveValues(cars = cars),
      scrm_outputs = reactive(iris)
    )
    
    
    # shinyWidgets::appendVerticalTab(
    #   inputId = "vtabwf_2", 
    #   shinyWidgets::verticalTabPanel(
    #     title = "duh", 
    #     shinydashboard::tabBox(
    #       width = 12,
    #       tabPanel(title = "Species 1", "species 1 outputs"),
    #       tabPanel(title = "Species 2", "species 2 outputs")
    #     )
    #   )
    # )
    # 
    # shinyWidgets::removeVerticalTab(
    #   inputId = "vtabwf_2",
    #   index = 1
    # )
    
  }

  shinyApp(ui, server)
}

output_panel_App()
```





## Functions

### Density Plots
```{r}
# Truncated Normal 
tnorm_dplot(mean = 0, sd = 0.5, xlab = "iiei", lower = 0)
tnorm_dplot(mean = 0.3, sd = .2, xlab = "iiei", lower = 0)


# Beta
beta_dplot(p = 1.1, sd = .05, xlab = "test")
```


### Quantile Tables
```{r}
tnorm_qtl_tbl(2, 3, lower =0, upper = Inf, varTag = "jjah", decPlaces = 3)

beta_qtl_tbl(p = 1, sd = 0.01, varTag = "gfdhs")
```



```{r}
string <- "abcefg ggafsffs ggggaggsh"
n <- 4

which(1:nchar(string) %% 2 == 0)


letter <- '<br/>'
lhs <- sprintf('^([a-z]{%d})([a-z]+)$', n-1) 
rhs <- paste0('\\1', letter, '\\2')
gsub(lhs, rhs, string)

```








## Plots


```{r}
stochLAB::wndspd_rtn_ptch_example %>%
  area_plot(x = wind_speed, y = rtn_speed, 
             xlab = "Wind Speed (m/s)", ylab = "Rotation speed (rpm)",
             point_col = "olivedrab", line_col = "gray", area_col = "olivedrab")

```



```{r}
startup_wind_avbl %>%
  tidyr::pivot_longer(cols = everything(), names_to = "month", values_to = "avlb") %>%
  mutate(month = factor(month, levels = month.name)) %>%
  lolli_plot(x = month, y = avlb, xlab = "Month", ylab = "Availability", 
             point_col = "olivedrab", line_col = "gray")
```





```{r}
fhd_boots_heatmap(
  data = stochLAB::generic_fhd_bootstraps$Black_legged_Kittiwake,
    height = height, 
    spp_label = "kittiwakinacio"
    )


```



```{r}

dt <- monthDens_pctls_template %>%
  mutate(across(January:December, .fns = ~qtnorm(p = Percentiles/100, mean = 3, sd = 1))) 

dt[, 2:13] <- dt[, 2:13] * matrix(1:12, nrow = 11, ncol = 12, byrow = TRUE)


densbird_pctl_plot(dt, pctl = Percentiles, spp_label = "kittuioioh")

dt %>%
  select(-c(May, September, November)) %>%
  densbird_pctl_plot(pctl = Percentiles, spp_label = "usujdbld")


dt %>%
  mutate(January = January[c(1:3, NA, 5:n())]) %>%
  densbird_pctl_plot(pctl = Percentiles, spp_label = "usujdbld")


dt %>%
  filter(Percentiles %in% c(2.5, 10, 75, 99)) %>%
  densbird_pctl_plot(pctl = Percentiles, spp_label = "boo")


```



```{r}
dt <- sapply(rnorm(12, 12, 6), function(x){
  rtnorm(1000, mean = x, sd = 1, lower = 0)
}) %>% 
  as_tibble() %>%
  rename_with(.fn = ~month.name)


densbird_draws_plot(
  data = dt, 
  spp_label = "gfdjkd"
)
```




```{r}
dist_df = tibble::tribble(
  ~month, ~subgroup, ~mean, ~sd,
  "a",          "h",     5,   1,
  "b",          "h",     7,   1.5,
  "c",          "h",     8,   1,
  "d",          "i",     9,   1,
  "f",          "j",     7,   1
)


dist_df %>%
  dplyr::mutate(
    dist = distributional::dist_truncated(
      distributional::dist_normal(mean, sd), 
      lower = 0)
  ) %>%
  dplyr::mutate(
    dist = 0.01 * (11 - dist)
  )%>%
  ggplot2::ggplot(ggplot2::aes(x = month, ydist = dist)) +
  ggdist::stat_pointinterval(
    colour = "green", 
    interval_size_range = c(1.5, 3),
    shape = 21,
    stroke = 1.5,
    point_size = 3,
    point_fill = "white",
    point_interval = "mean_qi") +
  ggplot2::labs(
    y = "Proportion of month operational", 
    title = "Mean and Quantile Intervals (66% and 95%) of proportion of time operational per month", 
    x = "")



dist_df %>%
  dplyr::mutate(
    dist = distributional::dist_truncated(
      distributional::dist_normal(mean, sd), 
      lower = 0)
  ) %>%
  dplyr::mutate(
    dist = 0.01 * (11 - dist),
    mean_tnorm = mean(dist)
  ) %>%
  ggplot2::ggplot(ggplot2::aes(x = month, ydist = dist)) +
  ggdist::stat_interval(
    interval_size = 10,
    .width = c(.5, .8, .95), #, .99)
    ) +
  ggplot2::geom_point(
    ggplot2::aes(x = month, y = mean_tnorm),
    size = 6,
    color = "#022601", #"#034701",
    ) +
  #ggplot2::scale_color_brewer(palette = "Greens", name = "Quantile Interval") +
  ggplot2::scale_color_manual(values = MetBrewer::met.brewer("VanGogh3", n = 3)) +
  ggplot2::labs(
    y = "Proportion of month operational", 
    title = "Mean and Quantile Intervals of proportion of time operational per month", 
    x = "")



```




## Developing final feedback table on input validation to grant simulation

```{r}

library(reactable)
library(tidyr)
library(dplyr)
library(tibble)


df <- tibble::tribble( 
  ~scenario,                  ~section, ~input_valid,
  "Demo WF",             "WF Features",         TRUE,
  "Demo WF",                "Demo SPP",         TRUE,
  "Demo WF",               "Kittiwake",        FALSE,
  "Tavira WF",           "WF Features",        FALSE,
  "Tavira WF",                  "Gull",         TRUE,
  "Veeeery Looong WF",   "WF Features",         TRUE,
  "Veeeery Looong WF",     "Razorbill",         TRUE,
  "Veeeery Looong WF",          "Gull",         TRUE,
  "Veeeery Looong WF",     "Kittiwake",         TRUE,
) 


df <- df %>%    
  dplyr::group_by(scenario) %>%
  dplyr::mutate(scenario_status = all(input_valid == TRUE)) %>%
  tidyr::nest(section_status = c("section", "input_valid"))


df %>%
  dplyr::select(scenario, scenario_status) %>%
  reactable::reactable(
    outlined = TRUE, 
    highlight = TRUE,
    theme = reactable::reactableTheme(borderColor = "black", headerStyle = "display: none"),
    columns = list(
      scenario = reactable::colDef(name = "Scenario", minWidth = 90),
      scenario_status = reactable::colDef(
        name = "Status", 
        minWidth = 60, 
        align = "center",
        cell = function(value) status_icon(value)
      )
    ),
    style = list(
      fontSize = "12px"
      #colour = "black"
    ),
    class = "hidden-column-headers",
    details = function(index){
      htmltools::div(
        style = "margin-left: 20px",
        reactable::reactable(
          df$section_status[[index]],
          theme = reactableTheme(backgroundColor = "#ebedf0"),
          columns = list(
            section =  reactable::colDef(name = "Input Section", minWidth = 90),
            input_valid = reactable::colDef(
              name = "", 
              minWidth = 60,
              align = "center",
              cell = function(value) status_icon(value))
          ),
          outlined = TRUE,
          highlight = TRUE
        )
      )
    }
  )






df <- tibble::tribble( 
                 ~scenario,   ~input_valid,
  "No scenarios specified",          FALSE
  
) 




df %>%
 reactable::reactable(
   theme = reactable::reactableTheme(borderColor = "black"),
   style = list(
     fontSize = "12px"
     #colour = "black"
   ),
   columns = list(
     #panel_id = reactable::colDef(show = FALSE),
     #section =  reactable::colDef(
    #   #name = "Input Section", 
    #   minWidth = 90
    # ),
     input_valid = reactable::colDef(
       #name = "", 
       minWidth = 40, 
       align = "center",
       cell = function(value, index) status_icon(value, level = 1)
     )
   ),
   outlined = TRUE
 )

```



## Automatic report generation
```{r}
run_datasets <- readr::read_rds("./data-raw/run_example_datasets_small.rds")

library(zeallot)
library(ggplot2)

c(scrm_inputs, scrm_outputs, scrm_results) %<-% run_datasets

rmarkdown::render(
  "inst/app/markdown/scrm_report/sCRM_report.rmd",
  params = list(
    scrm_inputs = scrm_inputs, 
    scrm_results = scrm_results,
    band_mode = FALSE,
    niter = 10
  ),
  envir = new.env(parent = globalenv())
)



wf_active <- scrm_inputs$active_scens

scrm_inputs$wf_scens$Demo_Windfarm$wf_inputs


```






## Devising structure of data to feed into `stochLAB::stoch_crm`


scrm_inputs
  |
  |- iv
  |
  |- scenario 1 (e.g. 'Demo_WF')
  |      |
  |      |- iv
  |      |
  |      |- input section 1 (e.g. 'wf_inputs')
  |      |       |
  |      |       |- iv
  |      |       |
  |      |       |- pars
  |      |            |
  |      |            |- pars section 1 (e.g. 'wf_ftrs')
  |      |            |- pars section 2 (e.g. 'trbn_ftrs')
  |      |
  |      |
  |      |- input section 2 (e.g. 'demo_spp_ftrs')
  |      |       |
  |      |       |- iv
  |      |       |
  |      |       |- pars
  |      |            |
  |      |            |- pars section 1 (e.g. 'bio_ftrs')
  |      |            |- pars section 2 (e.g. 'fhd')
  |      |            |- ...
  |      |
  |      |- ...
  |
  |
  |- scenario 2 (e.g. 'Berwick_Bank')
  |      |
  |      |- iv
  |      |
  |      |- input section 1
  |      |       |
  |      |       |- iv
  |      |       |
  |      |       |- pars
  |      |
  |      |- ...
  |      
  |- ...      
  
  
  
```{r}




scrm_inputs <- list(list(list()))

scrm_inputs[["demo_wf"]][["wf_inputs"]][["iv"]] <- "test"


scrm_inputs[["demo_wf"]][["wf_inputs"]][["wf_ftrs"]] <- 
  data.frame(
    n_turbines = 3,
    latitude = 55,
    width = 10
  )


scrm_inputs[["demo_wf"]][["wf_inputs"]][["trbn_ftrs"]] <-
  tibble::tibble(
    n_blades = 3,
    rtr_radius = 12,
    air_gap = 7,
    rtn_pitch = list(  
      parlist = list(
        opt = "prob",
        bldptch = tibble::tibble(mean = 3, sd = 1),
        rtr_speed = tibble::tibble(mean = 10, sd = 2)  
      )
    )
  )
    

scrm_inputs$demo_wf$wf_inputs$trbn_ftrs$rtn_pitch$parlist$opt




test <- list(
  valid = TRUE,
  scen_1 = list(
    valid = TRUE,
    wf_label = "scenario 1",
    wf_tbpnl = "tbx-pnl-scen1",
    wf_inputs = list(
      valid = TRUE,
      wf_ftrs = list(
        nturb = 100,
        lat = 45
      ),
      trb_ftrs = list(
        n_blades = 2,
        airgap = 12
      )
    ),
    demo_spp = list(
      valid = TRUE,
      biom_ftrs = list(
        bodylt = data.frame(mean = 12, sd = 2),
        wing_span =  data.frame(mean = 5, sd = 2)
      ),
      fhd = data.frame(height = 1:100, matrix(0, nrow = 100, ncol = 100)),
      inflight_ftrs = list(
        fltype = "Gliding",
        crh = 12
      ),
      bdens = data.frame(month = month.name, mean = 1:12, sd = 1)
    )
  )
)


test$valid <- NULL

purrr::pluck(test, "valid") <- NULL


```




## TO DO's and to Check

- `dashboardBadge` to sidebar items indicating the number of items in each
section (e.g. number of windfarms; number of species in a windfarm scenario)

- Activate "Close/Done" button on Add Species dropdown bubble

- FIX: issue with reselecting previously removed windfarm

- FIX: extra vertical tabs for generic and site-specific FHDs are being added
every time a species is selected repeatedly







## UI items id tagging conventions

Tags must always be separated by `_`

1. UI element type:
  - `actionButton` and alike: 'btn_' + *action*, as *action* is inherent to buttons.
  Choices for *actions*:
    - 'add', 'rmv', 'upd', 'run', etc.
  - `tabBox`: 'tbx'
  - `tabPanel`: 'tbp'
  - `sidebarMenu`: 'sbm'
  - `menuSubItem`: 'msi'
  - `selectizeInpu`: 'sltz'

2. Section:
  - Windfarm/turbine scenarios: 'wf'
  - Species features: 'spp'
  - Simulation: 'sim'

3. Scenario or species ID, e.g:
  - Windfarm scenario '1': '1'
  - Kitiwake: 'kitti'

> NOTE: scenario IDs currently numeric, automatically assigned as scenario is
added by the client. This is convenient for managing id's based on their recency.
  
4. Parameter-level ID, e.g.:
  - no. turbines: 'n_turb',
  - bird length: 'lt'
  

E.g: 'btn_rmv_wf_2': Button that removes the panel for WF scenario 2



  
  

